Designing Types for R, Empirically

### 2020-05-16 paper/main.tex
types

type `dplyr::group\_indices` <class<`data.frame`>, ...> => integer[];

type `lava::index` <class<`lvm`> | class<`lvmfit`>, ...> => (null | list<any>);

type `diptest::dip` <double[], character | logical, logical, double> => (class<`dip`> | double);

type `stabledist::cospi2` <double[]> => double[];

type `emplik::llogp` <class<`matrix`> | double[], double> => (class<`matrix`> | double[]);

>>>>

\code{dplyr::group_indices}: \FUN{\CLASS{data.frame}, \VARGS}{\VEC\int}

\code{lava::index}: \FUN{\CLASS{lvm} \; | \; \CLASS{lvmfit}, \VARGS}{\; ? \; \LIST{any}}

\code{diptest::dip}: \FUN{\VEC\dbl, \chr \; | \; \lgl, \lgl, \dbl}{\CLASS{dip} \; | \; \dbl}

\code{stabledist::cospi2}: \FUN{\VEC\dbl}{\VEC\dbl}

\code{matrixcalc::matrix.power}: \FUN{\CLASS{matrix}, \dbl}{\CLASS{matrix}}
